Titeln på avhandlingens språk

### 2023-05-12 body/acks.tex
acks

This dissertation would not have been possible without the help and support of my family.
First and foremost, I would like to thank the love of my life and wife~\footnote{\emph{Future-wife} at the time of writing, but \emph{wife} at the time of the defense of this thesis!}, Andresa.
I could not have done this without her companionship and love.
I am eternally grateful for her unconditional support over difficult periods of time and over tremendous distances while we were living apart, and for making every day we spend together amazing.

I am also deeply grateful to my parents, Gabriel and Valeria, for always encouraging my curiosity and my drive to learn and discover.
They have been my rocks, my pillars, since the day I was born, and I am proud to be their son.
A big thank you goes out to my sister, Paola, as well.
Although we sometimes get on each other's nerves, she has always been there for me and supported me, and I could not have asked for a better sister.
Likewise, I extend my deepest gratitude to everyone in my immediate and extended family who have given me support and love over the years, including but not limited to my paternal grandparents, Manuel and María Yolanda, my maternal grandparents, Caupolicán and María Aura, my uncle Mauricio, his wife Marylen, their daughter Amanda, and everybody else.
I would like to make a special mention to my late grandfather, Caupolicán ``Poli'' Muñoz, who always inspired and fanned the flames of academic curiosity in me.
I hope he would have been proud seeing how far I have come.
Another special mention goes to my uncle Manuel, who graciously took me in and gave me a place to stay at the first few months of my Ph.D. studies.

I would also like to thank all of my friends who have made this long, ardous journey more amenable.
I would particularly like to thank everyone I met through Tartan Salsa, including, but not limited to, Andresa, Jennifer, Alyson, Kuai-Kuai, Carmen, Moataz and Nora, Eric, and many others.
They made Pittsburgh feel like home, even before I finally moved there permanently in 2022.
I also want to thank Ann-Charlotte in Stockholm, for always being so kind, so considerate, and so much fun to be around.
Further, I am deeply grateful to my friends in Chile who have remained a source of support, even though we only get to see each other once a year when I visit.
This includes, but is not limited to, Juan Pablo, Fernanda, Diego, Camila, George, Patricio, Kevin, Pablo, and many others.
Yet another special mention goes to Diego's family, who have always treated me as one of their own.

@@

\bigskip

\noindent{}Manuel Olguín Muñoz\\
Pittsburgh, May 2023

>>>>

This dissertation would not have been possible without the help and support of my family.
First and foremost, I would like to thank the love of my life and wife~\footnote{\emph{Future-wife} at the time of writing, but \emph{wife} at the time of the defense of this thesis!}, Andresa.
I could not have done this without her companionship and love.
I am eternally grateful for her unconditional support over difficult periods of time and over tremendous distances while we were living apart, and for making every day we spend together amazing.
I am also deeply grateful to my parents, Gabriel and Valeria, for always encouraging my curiosity and my drive to learn and discover.
They have been my rocks, my pillars, since the day I was born, and I am proud to be their son.
A big thank you goes out to my sister, Paola, as well.
Although we sometimes get on each other's nerves, she has always been there for me and supported me, and I could not have asked for a better sister.
Likewise, I extend my deepest gratitude to everyone in my immediate and extended family who have given me support and love over the years, including but not limited to my paternal grandparents, Manuel and María Yolanda, my maternal grandparents, Caupolicán and María Aura, my uncle Mauricio, his wife Marylen, their daughter Amanda, and everybody else.
I would like to make a special mention to my late grandfather, Caupolicán ``Poli'' Muñoz, who always inspired and fanned the flames of academic curiosity in me.
I hope he would have been proud seeing how far I have come.
Another special mention goes to my uncle Manuel, who graciously took me in and gave me a place to stay at the first few months of my Ph.D. studies.

I would also like to thank all of my friends who have made this long, arduous journey more amenable.
I would particularly like to thank everyone I met through Tartan Salsa, including, but not limited to, Andresa, Jennifer, Alyson, Carmen, Kuai-Kuai and Eric, Moataz and Nora, and many others.
\todo[inline]{Special mention Jenn and Alyson?}
They made Pittsburgh feel like home, even before I finally moved there permanently in 2022.
I also want to thank Ann-Charlotte in Stockholm, for always being so kind, so considerate, and so much fun to be around.
Further, I am deeply grateful to my friends in Chile who have remained a source of support, even though we only get to see each other once a year when I visit.
This includes, but is not limited to, Juan Pablo, Fernanda, Diego, Camila, George, Patricio, Kevin, Pablo, and many others.
Yet another special mention goes to Diego's family, who have always treated me as one of their own.

@@

\medskip
{\begin{flushright}
    Manuel Olguín Muñoz, May 2023
\end{flushright}}
